---
title: "rsofun runs for optimal temperature data"
author: "Pascal Schneider"
output: html_document
---

# Benchmark of opt. temperature via observations
## Description

- Please make sure to use rsofun version 3.4 to run code below

## Load data
```{r}
library(rsofun)
library(ingestr)
library(tidyverse)
```

```{r}
load("~/data/rsofun_benchmarking/df_drivers_topt_v3.4.Rdata")
```

- There seem to be some leap year dates which create problems for rsofun. Drop Feb. 29 dates.

```{r}
df_drivers_topt <- df_drivers_topt %>% 
  dplyr::select(sitename, forcing) %>% 
  unnest(forcing) %>% 
  dplyr::filter(!(month(date)==2 & mday(date)==29)) %>% 
  group_by(sitename) %>% 
  nest() %>%
  rename(forcing = data) %>% 
  right_join(
    df_drivers_topt %>% 
      dplyr::select(-forcing),
    by = "sitename"
  ) %>% 
  ungroup()
```


## Calibrate model

- This is taken from the rsofun version 3.4 calibration using Fluxnet:

```{r}
params_modl <- list(
	kphio           = 0.05,
	soilm_par_a     = 1.0,
	soilm_par_b     = 0.0,
	vpdstress_par_a = 9999,
	vpdstress_par_b = 9999,
	vpdstress_par_m = 9999
	)

load("~/data/rsofun_benchmarking/settings_calib_v3.4.Rdata")

params_modl <- update_params(params_modl, settings_calib)
```


## Run model
```{r  warning=FALSE, message=FALSE, error=FALSE}
detach("package:rsofun", unload = TRUE)
library(rsofun)

df_output <- runread_pmodel_f(
     df_drivers = df_drivers_topt,
     params_modl = params_modl, 
     makecheck = TRUE,
     parallel = FALSE
     )

# Save output
# saveRDS(df_output, "~/data/mscthesis/final/rsofun_v3.4_topt_k19_tau30.rds")
```


## Evaluation results

Load observed optimal temperature data
```{r}
load("~/data/rsofun_benchmarking/obs_eval_topt_v3.4.Rdata")
```

```{r}
df_topt_eval <- left_join(obs_eval_topt,
                          df_output %>%
                              unnest(data) %>% 
                              rename(tc_opt_sim = topt),
                          by = c("sitename", "date"))
```


### Metrics
```{r error=FALSE, message=FALSE, warning=FALSE, include=FALSE}
fit   <- lm(tc_opt_obs ~ tc_opt_sim, data = df_topt_eval)
sry   <- summary(fit)
r2    <- sry$adj.r.squared %>% round(2)
rmse  <- sqrt( ( c(crossprod(sry$residuals)) / length(sry$residuals) ) ) %>% round(2)
slope <- sry$coefficients[2, 1] %>% round(2)
b0_sign <- sry$coefficients[1, 4] <= 0.05 # T = Intercept is signficantly different from 0
b1_sign <- !(between(1, confint(fit, 'tc_opt_sim', level=0.95)[1] %>% round(2), confint(fit, 'tc_opt_sim', level=0.95)[2]) %>% round(2)) # T = Slope is significantly different from 1
bias  <- mean(df_topt_eval$tc_opt_sim - df_topt_eval$tc_opt_obs) %>% round(2)
```


```{r error=FALSE, message=FALSE, warning=FALSE}
lm(tc_opt_obs ~ tc_opt_sim, data = df_topt_eval) %>% summary()
```


### Visualisations
```{r}
df_topt_eval %>% 
    ggplot() +
    aes(x = tc_opt_sim, y = tc_opt_obs) +
	geom_abline(linetype = "dotted") +
    geom_point() +
	geom_smooth(method = "lm", size = 0.5, fullrange = T, color = "red") +
	xlim(0, 40) +
	ylim(0, 40) +
	xlab(bquote("Predicted " ~ T[opt] ~ " [°C]")) +
	ylab(bquote("Observed " ~ T[opt] ~ " [°C]")) +
	labs(title = "Optimal Temperature",
		 subtitle = bquote(R^2  ~  " = "  ~ .(r2)  ~  " | bias = "  ~ .(bias)  ~  " | slope = "  ~ .(slope) ~  " | RMSE = "  ~ .(rmse))) +
    theme_classic()
```

