---
title: "Analysis of Acclimated P-Model Setups"
date: "`r Sys.Date()`"
author: "Pascal Schneider"
output:
  rmdformats::downcute:
    code_folding: hide
    lightbox: true
    gallery: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	error = FALSE,
	message = FALSE,
	warning = FALSE,
	cache = TRUE
)
suppressMessages(source("~/projects/mscthesis/scripts/final/source_fct_pkg.R"))
```


# Sanity check with rsofun output
```{r, fig.height=2.75, fig.width=8}
## Getting driver and evaluation data
load("~/data/rsofun_benchmarking/df_drivers_topt_v3.4.Rdata")
df_drivers_k19     <- df_drivers_topt
df_evaluation_k19  <- readRDS("~/data/mscthesis/final/df_obs_opt_postQC.rds")


## Run acclimated P-Model
settings <- get_settings()
df_accl  <- run_rpmodel_accl(settings = settings, df_drivers = df_drivers_k19, df_evaluation = df_evaluation_k19, target_var = target_var)


## Select variables from acclimated rsofun
vars_ <- c("vcmax", "jmax", "vcmax25", "jmax25", "tc_growth_air", "kphio", "xi") # "vcmax", "jmax", "vcmax25", "jmax25", "tc_growth_air", "kphio", "xi"
df_rsof <- df_accl %>%
    dplyr::select(sitename, date) %>% 
    left_join(readRDS("~/data/mscthesis/final/rsofun_v3.4_topt_k19_tau30.rds") %>% unnest(data)) %>% 
    dplyr::select(sitename, date, vcmax, jmax, vcmax25, jmax25, debug1, debug2) %>% 
    rename(tc_growth_air = debug1,
           kphio         = debug2) %>% 
    mutate(vcmax = vcmax/max(vcmax),
       jmax  = jmax /max(jmax ),
       vcmax25 = vcmax25/max(vcmax25),
       jmax25  = jmax25 /max(jmax25 ),
       tc_growth_air = tc_growth_air/max(tc_growth_air),
       kphio = kphio/max(kphio)) %>% 
    pivot_longer(cols = any_of(vars_), names_to = "variable", values_to = "rsofun")


## Select variables from acclimated rpmodel
df_rpm <- df_accl %>%
    unnest(c(rpm_accl, forcing)) %>% 
    dplyr::select(sitename, date, vcmax, jmax, vcmax25, jmax25, tc_growth_air, kphio) %>% 
    mutate(vcmax = vcmax/max(vcmax),
           jmax  = jmax /max(jmax ),
           vcmax25 = vcmax25/max(vcmax25),
           jmax25  = jmax25 /max(jmax25 ),
           tc_growth_air = tc_growth_air/max(tc_growth_air),
           kphio = kphio/max(kphio)) %>% 
    pivot_longer(cols = any_of(vars_), names_to = "variable", values_to = "rpmodel")

    
## Connect and plot both data frames
(p <- left_join(df_rsof, df_rpm) %>% 
    dplyr::filter(variable != "jmax",
                  variable != "vcmax") %>%
    ggplot() +
    aes(x = rsofun, y = rpmodel) +
    geom_abline(linetype = "dotted") +
    geom_point() +
    geom_smooth(method = "lm") +
    ylab("Normalized prediction using R [-]") +
    xlab("Normalized prediction using Fortran [-]") +
    facet_wrap( ~ variable, ncol = 4) +
    ggpmisc::stat_poly_eq(formula = y ~ x,
                          aes(label = paste(..eq.label.., sep = "~~~")),
                          parse = TRUE,
                          vjust = 1) +
    ggpmisc::stat_poly_eq(formula = y ~ x,
                          aes(label = paste(..rr.label.., sep = "~~~")),
                          parse = TRUE,
                          vjust = 2.5))


# ggsave("~/projects/mscthesis/docs/fig_comparison_r_fortran.pdf", p, height = 2.75, width = 8)
```


# Analytical vs. numerical
## Get driver and evaluation data
```{r}
df_drivers_p21    <- readRDS("~/data/mscthesis/final/df_drivers_p21.rds")
df_evaluation_p21 <- readRDS("~/data/mscthesis/raw/leaf_traits_peng2021/df_P21_clean_with_cl.rds") %>%
    dplyr::select(-author) %>%
    rename_with(tolower) %>%
    dplyr::filter(!(is.na(vcmax) & is.na(jmax)),
                  !is.na(date),
                  !is.na(lat),
                  !is.na(lon),
                  date != "2053-05-11",
                  date != "2081-08-27") %>%
    group_by(site, date) %>%
    nest() %>%
    ungroup() %>%
    rename(sitename = site,
           data_raw = data)
```

## Smith37
```{r fig.height=6, fig.width=8}
## Analytical
settings <- get_settings()
df_ana_s37   <- run_rpmodel_accl(settings = settings,
                                 df_drivers = df_drivers_p21,
                                 df_evaluation = df_evaluation_p21) %>%
    get_instant_vcmax_jmax(ftemp_method = settings$rpmodel_accl$method_ftemp)

p_ana_s37    <-
    plot_two_long_df(
        df_x = make_long_df(df_in = df_ana_s37, dataset = "analytical_s37"),
        df_x_dataset = "analytical_s37",
        df_y = make_df_evaluation_p21_long(df_in = df_ana_s37),
        df_y_dataset = "peng21",
        kphio_vcmax_corr = F
    )
    

## Numerical
settings <- get_settings()
settings$rpmodel_accl$method_optim  <- "numerical"
df_num_s37 <- run_rpmodel_accl(settings = settings,
                               df_drivers = df_drivers_p21,
                               df_evaluation = df_evaluation_p21) %>%
    get_instant_vcmax_jmax(ftemp_method = settings$rpmodel_accl$method_ftemp)

p_num_s37  <-
    plot_two_long_df(
        df_x = make_long_df(df_in = df_num_s37, dataset = "numerical_s37"),
        df_x_dataset = "numerical_s37",
        df_y = make_df_evaluation_p21_long(df_in = df_num_s37),
        df_y_dataset = "peng21",
        kphio_vcmax_corr = F
    )


## Plots
p_ana_s37 <- p_ana_s37 + xlim(0, 250) + ylim(0, 250)
p_num_s37 <- p_num_s37 + xlim(0, 250) + ylim(0, 250)

p_ana_s37/p_num_s37 + plot_layout(guides = "collect") & theme(legend.position = "bottom")
```


## Farquhar89
```{r fig.height=6, fig.width=8}
## Analytical
settings <- get_settings()
settings$rpmodel_accl$method_jmaxlim <- "farquhar89"
df_ana_f89   <-
    run_rpmodel_accl(settings = settings,
                     df_drivers = df_drivers_p21,
                     df_evaluation = df_evaluation_p21) %>%
    get_instant_vcmax_jmax(ftemp_method = settings$rpmodel_accl$method_ftemp)

p_ana_f89    <-
    plot_two_long_df(
        df_x = make_long_df(df_in = df_ana_f89, dataset = "analytical_f89"),
        df_x_dataset = "analytical_f89",
        df_y = make_df_evaluation_p21_long(df_in = df_ana_f89),
        df_y_dataset = "peng21",
        kphio_vcmax_corr = T
    )


## Numerical
settings <- get_settings()
settings$rpmodel_accl$method_jmaxlim <- "farquhar89"
settings$rpmodel_accl$method_optim <- "numerical"
df_num_f89 <-
    run_rpmodel_accl(settings = settings,
                     df_drivers = df_drivers_p21,
                     df_evaluation = df_evaluation_p21) %>%
    get_instant_vcmax_jmax(ftemp_method = settings$rpmodel_accl$method_ftemp)

p_num_f89  <-
    plot_two_long_df(
        df_x = make_long_df(df_in = df_num_f89, dataset = "numerical_f89"),
        df_x_dataset = "numerical_f89",
        df_y = make_df_evaluation_p21_long(df_in = df_num_f89),
        df_y_dataset = "peng21",
        kphio_vcmax_corr = F
    )


## Plots
p_ana_f89 <- p_ana_f89 + xlim(0, 250) + ylim(0, 250)
p_num_f89 <- p_num_f89 + xlim(0, 250) + ylim(0, 250)

p_ana_f89 / p_num_f89 + plot_layout(guides = "collect") & theme(legend.position = "bottom")
```


## ENERGY BALANCE
```{r fig.height=6}
## Analytical
settings <- get_settings()
t_start <- Sys.time()
df_dummy <- run_rpmodel_accl(settings = settings, df_drivers = df_drivers_p21, df_evaluation = df_evaluation_p21) %>% get_instant_vcmax_jmax(ftemp_method = settings$rpmodel_accl$method_ftemp)
t_ana <- difftime(Sys.time(), t_start, units = "min") %>% round(2)


## Numerical, no EB
settings$rpmodel_accl$method_optim <- "numerical"
t_start <- Sys.time()
df_noeb <- run_rpmodel_accl(settings = settings, df_drivers = df_drivers_p21, df_evaluation = df_evaluation_p21) %>% get_instant_vcmax_jmax(ftemp_method = settings$rpmodel_accl$method_ftemp)
t_noeb <- difftime(Sys.time(), t_start, units = "min") %>% round(2)
p_noeb  <- plot_two_long_df(
    df_x = make_long_df(df_in = df_noeb, dataset = "no_energy_balance"),
    df_x_dataset = "no_energy_balance",
    df_y = make_df_evaluation_p21_long(df_in = df_noeb),
    df_y_dataset = "peng21",
    kphio_vcmax_corr = F
)



## EB via plantecophys
settings$rpmodel_accl$method_eb <- "plantecophys"
t_start <- Sys.time()
df_eb_pl <- run_rpmodel_accl(settings = settings, df_drivers = df_drivers_p21, df_evaluation = df_evaluation_p21) %>% get_instant_vcmax_jmax(ftemp_method = settings$rpmodel_accl$method_ftemp)
t_eb_pl <- difftime(Sys.time(), t_start, units = "min") %>% round(2)
p_eb_pl  <- plot_two_long_df(
    df_x = make_long_df(df_in = df_eb_pl, dataset = "eb_plantecophys"),
    df_x_dataset = "eb_plantecophys",
    df_y = make_df_evaluation_p21_long(df_in = df_eb_pl),
    df_y_dataset = "peng21",
    kphio_vcmax_corr = F
)


## EB via tealeaves
t_start <- Sys.time()
settings$rpmodel_accl$method_eb <- "tealeaves"
t_start <- Sys.time()
df_eb_te <- run_rpmodel_accl(settings = settings, df_drivers = df_drivers_p21, df_evaluation = df_evaluation_p21) %>% get_instant_vcmax_jmax(ftemp_method = settings$rpmodel_accl$method_ftemp)
t_eb_te <- difftime(Sys.time(), t_start, units = "min") %>% round(2)
p_eb_te  <- plot_two_long_df(
    df_x = make_long_df(df_in = df_eb_te, dataset = "eb_tealeaves"),
    df_x_dataset = "eb_tealeaves",
    df_y = make_df_evaluation_p21_long(df_in = df_eb_te),
    df_y_dataset = "peng21",
    kphio_vcmax_corr = F
)


## Computing time (run in console directly is quicker than in chunk!)
cat(" Computation time: \n",
    "_______________________________ \n",
    "Analytical Model:      ", paste0(t_ana), "min. \n", #ifelse(t_ana > 1, paste0(t_ana, " min"), paste0(t_ana*60, " sec")), "\n",
    "Numerical Model:       ", paste0(t_noeb), "min. \n", #ifelse(t_noeb > 1, paste0(t_noeb, " min"), paste0(t_noeb*60, " sec")), "\n",
    "Num. + Planteco Model: ", paste0(t_eb_pl), "min. \n", #ifelse(t_eb_pl > 1, paste0(t_eb_pl, " min"), paste0(t_eb_pl*60, " sec")), "\n",
    "Num. + tealeaves Model:", paste0(t_eb_te), "min. \n") #ifelse(t_eb_te > 1, paste0(t_eb_te, " min"), paste0(t_eb_te*60, " sec")), "\n")



## Plots
# p1 <- p_noeb +  xlim(0, 250) + ylim(0, 250) + theme(legend.position = "bottom")
# p2 <- p_eb_pl + xlim(0, 250) + ylim(0, 250) + theme(legend.position = "bottom")
# p3 <- p_eb_te + xlim(0, 250) + ylim(0, 250) + theme(legend.position = "bottom")
# 
# p1 + p2 + p3 + plot_layout(guides = "collect") & theme(legend.position = "bottom")
p1 / p2
```


# Analysis of s37 + numeric
## Kattge07 vs. Kumarathunge19
```{r}
## Kumarathunge19
settings <- get_settings()
settings$rpmodel_accl$method_optim <- "numerical"
df_k19 <- run_rpmodel_accl(settings = settings, df_drivers = df_drivers_p21, df_evaluation = df_evaluation_p21) %>% get_instant_vcmax_jmax(ftemp_method = settings$rpmodel_accl$method_ftemp)
p_k19  <- plot_two_long_df(df_x = make_long_df(df_in = df_k19, dataset = "kumarathunge19"), df_x_dataset = "kumarathunge19", df_y = make_df_evaluation_p21_long(df_in = df_k19), df_y_dataset = "peng21")


## Kattge07
settings$rpmodel_accl$method_ftemp <- "kattge07"
df_k07 <- run_rpmodel_accl(settings = settings, df_drivers = df_drivers_p21, df_evaluation = df_evaluation_p21) %>% get_instant_vcmax_jmax(ftemp_method = settings$rpmodel_accl$method_ftemp)
p_k07  <- plot_two_long_df(df_x = make_long_df(df_in = df_k07, dataset = "kattge07"), df_x_dataset = "kattge07", df_y = make_df_evaluation_p21_long(df_in = df_k07), df_y_dataset = "peng21")


## Plots
p_k19 + xlim(0, 6e-4) + ylim(0, 6e-4)
p_k07 + xlim(0, 6e-4) + ylim(0, 6e-4)
```


## Acclimation time-spans
```{r}
## Reference: All tau = 30:
settings <- get_settings()
settings$rpmodel_accl$method_optim <- "numerical"
df_all_30 <- run_rpmodel_accl(settings = settings, df_drivers = df_drivers_p21, df_evaluation = df_evaluation_p21)  %>%
    get_instant_vcmax_jmax(ftemp_method = settings$rpmodel_accl$method_ftemp)
p_all_30  <- plot_two_long_df(df_x = make_long_df(df_in = df_all_30, dataset = "all_tau_30"), df_x_dataset = "all_tau_30", df_y = make_df_evaluation_p21_long(df_in = df_all_30), df_y_dataset = "peng21", kphio_vcmax_corr = F)


## Shorter thermal acclimation: tc_air_tau = 10:
settings$rpmodel_accl$tau$tc_air <- 10
df_temp10 <- run_rpmodel_accl(settings = settings, df_drivers = df_drivers_p21, df_evaluation = df_evaluation_p21) %>% get_instant_vcmax_jmax(ftemp_method = settings$rpmodel_accl$method_ftemp)
p_temp10  <- plot_two_long_df(df_x = make_long_df(df_in = df_temp10, dataset = "temp_tau_10"), df_x_dataset = "temp_tau_10", df_y = make_df_evaluation_p21_long(df_in = df_temp10), df_y_dataset = "peng21", kphio_vcmax_corr = F)


## Shorter light acclimation: ppfd_tau = 10:
settings$rpmodel_accl$tau$tc_air <- 30
settings$rpmodel_accl$tau$ppfd   <- 10
df_ppfd10 <- run_rpmodel_accl(settings = settings, df_drivers = df_drivers_p21, df_evaluation = df_evaluation_p21) %>% get_instant_vcmax_jmax(ftemp_method = settings$rpmodel_accl$method_ftemp)
p_ppfd10  <- plot_two_long_df(df_x = make_long_df(df_in = df_ppfd10, dataset = "ppfd_tau_10"), df_x_dataset = "ppfd_tau_10", df_y = make_df_evaluation_p21_long(df_in = df_ppfd10), df_y_dataset = "peng21", kphio_vcmax_corr = F)


## Shorter thermal & light acclimation: temp_tau = ppfd_tau = 10:
settings$rpmodel_accl$tau$tc_air <- 10
df_tempppfd30 <- run_rpmodel_accl(settings = settings, df_drivers = df_drivers_p21, df_evaluation = df_evaluation_p21) %>% get_instant_vcmax_jmax(ftemp_method = settings$rpmodel_accl$method_ftemp)
p_tempppfd30  <- plot_two_long_df(df_x = make_long_df(df_in = df_tempppfd30, dataset = "temp_ppfd_tau_10"), df_x_dataset = "temp_ppfd_tau_10", df_y = make_df_evaluation_p21_long(df_in = df_tempppfd30), df_y_dataset = "peng21", kphio_vcmax_corr = F)


## Plots
p_all_30     + xlim(0, 250) + ylim(0, 250) + theme(legend.position = "bottom")
p_temp10     + xlim(0, 250) + ylim(0, 250) + theme(legend.position = "bottom")
p_ppfd10     + xlim(0, 250) + ylim(0, 250) + theme(legend.position = "bottom")
p_tempppfd30 + xlim(0, 250) + ylim(0, 250) + theme(legend.position = "bottom")

## Notes
# tc_air tau = 5  -> r'2 0.59
# tc_air tau = 15 -> r'2 0.60
# tc_air tau = 30 -> r'2 0.74
# tc_air tau = 45 -> r'2 0.72

```

```{r}
df_drivers_p21 %>% unnest(forcing) %>% ggplot(aes(doy, ppfd)) + geom_point(alpha = 0.25) + facet_wrap(~sitename)
```



# Final Model
```{r}
## Best model:
settings <- get_settings()
settings$rpmodel_accl$method_optim <- "numerical"
settings$rpmodel_accl$method_eb <- "tealeaves"
settings$rpmodel_accl$tau$tc_air <- 5


t_start <- Sys.time()
df_best <- run_rpmodel_accl(settings = settings, df_drivers = df_drivers_p21, df_evaluation = df_evaluation_p21) %>% get_instant_vcmax_jmax(ftemp_method = settings$rpmodel_accl$method_ftemp)
p_best  <- plot_two_long_df(df_x = make_long_df(df_in = df_best, dataset = "num_s37_planteco_temp10"), df_x_dataset = "num_s37_planteco_temp10", df_y = make_df_evaluation_p21_long(df_in = df_best), df_y_dataset = "peng21")
t_dur   <- Sys.time() - t_start


t_dur
p_best
```




# ---
# >> Plots for thesis
## Analytical Models
```{r fig.height=4.25, fig.width=8}
# RUN MODELS........................................................................................
## Smith:
settings <- get_settings()
df_ana_s37   <- run_rpmodel_accl(settings = settings,
                                 df_drivers = df_drivers_p21,
                                 df_evaluation = df_evaluation_p21) %>% 
    get_instant_vcmax_jmax(., ftemp_method = settings$rpmodel_accl$method_ftemp)


## Farquhar:
settings <- get_settings()
settings$rpmodel_accl$method_jmaxlim <- "farquhar89"
df_ana_f89 <- run_rpmodel_accl(settings = settings,
                               df_drivers = df_drivers_p21,
                               df_evaluation = df_evaluation_p21) %>% 
    get_instant_vcmax_jmax(., ftemp_method = settings$rpmodel_accl$method_ftemp)

# RUN PLOT FUNCTIONS ...............................................................................
## Smith:
p_ana_s37    <-
    plot_two_long_df(
        df_x = make_long_df(df_in = df_ana_s37, dataset = "analytical_s37"),
        df_x_dataset = "analytical_s37",
        df_y = make_df_evaluation_p21_long(df_in = df_ana_s37),
        df_y_dataset = "peng21",
        kphio_vcmax_corr = F,
        return_separate = T,
        model = "Smith"
    )

## Farquhar:
p_ana_f89    <-
    plot_two_long_df(
        df_x = make_long_df(df_in = df_ana_f89, dataset = "analytical_f89"),
        df_x_dataset = "analytical_f89",
        df_y = make_df_evaluation_p21_long(df_in = df_ana_f89),
        df_y_dataset = "peng21",
        kphio_vcmax_corr = F,
        return_separate = T,
        model = "Farquhar"
    )

# CALL PLOTS .......................................................................................
# VCMAX
(p <- p_ana_s37$pvcmax + p_ana_f89$pvcmax + ylab("") +
    plot_layout(guides = "collect")  &
    theme(legend.position = "bottom", legend.justification = "center"))

ggsave("~/projects/mscthesis/docs/fig_comparison_analytic_vcmax.pdf", plot = p, height = 4.5, width = 8)

# JMAX
(p <- p_ana_s37$pjmax + p_ana_f89$pjmax + ylab("") +
    plot_layout(guides = "collect")  &
    theme(legend.position = "bottom", legend.justification = "center"))

# ggsave("~/projects/mscthesis/docs/fig_comparison_analytic_jmax.pdf", plot = p, height = 4.75, width = 8)
```

## Numerical Models
```{r fig.height=4.25, fig.width=8}
# RUN MODELS........................................................................................
## Smith:
settings <- get_settings()
settings$rpmodel_accl$method_optim <- "numerical"
df_num_s37   <- run_rpmodel_accl(settings = settings,
                                 df_drivers = df_drivers_p21,
                                 df_evaluation = df_evaluation_p21) %>% 
    get_instant_vcmax_jmax(., ftemp_method = settings$rpmodel_accl$method_ftemp)


## Farquhar:
settings <- get_settings()
settings$rpmodel_accl$method_jmaxlim <- "farquhar89"
settings$rpmodel_accl$method_optim <- "numerical"
df_num_f89 <- run_rpmodel_accl(settings = settings,
                               df_drivers = df_drivers_p21,
                               df_evaluation = df_evaluation_p21) %>% 
    get_instant_vcmax_jmax(., ftemp_method = settings$rpmodel_accl$method_ftemp)

# RUN PLOT FUNCTIONS ...............................................................................
## Smith:
p_num_s37    <-
    plot_two_long_df(
        df_x = make_long_df(df_in = df_num_s37, dataset = "analytical_s37"),
        df_x_dataset = "analytical_s37",
        df_y = make_df_evaluation_p21_long(df_in = df_num_s37),
        df_y_dataset = "peng21",
        kphio_vcmax_corr = F,
        return_separate = T,
        model = "Smith"
    )

## Farquhar:
p_num_f89    <-
    plot_two_long_df(
        df_x = make_long_df(df_in = df_num_f89, dataset = "analytical_f89"),
        df_x_dataset = "analytical_f89",
        df_y = make_df_evaluation_p21_long(df_in = df_num_f89),
        df_y_dataset = "peng21",
        kphio_vcmax_corr = F,
        return_separate = T,
        model = "Farquhar"
    )

# CALL PLOTS .......................................................................................
# VCMAX
(p <- p_num_s37$pvcmax + p_num_f89$pvcmax + ylab("") +
    plot_layout(guides = "collect")  &
    theme(legend.position = "bottom", legend.justification = "center"))

ggsave("~/projects/mscthesis/docs/fig_comparison_numeric_vcmax.pdf", plot = p, height = 4.25, width = 8)

# JMAX
(p <- p_num_s37$pjmax + p_num_f89$pjmax + ylab("") +
    plot_layout(guides = "collect")  &
    theme(legend.position = "bottom", legend.justification = "center"))

# ggsave("~/projects/mscthesis/docs/fig_comparison_numeric_jmax.pdf", plot = p, height = 4.25, width = 8)
```

## ENERGY BALANCE
### All models
```{r, fig.height=7, fig.width=8}
# From background job -> run energy-balance chunk above with "farquhar89" setting -> little difference
ptitle <- "Energy Balance | Numerical | Farquhar-Formulation"
p_noeb <- background_jobs_results[["p_noeb"]]
p_eb_pl <- background_jobs_results[["p_eb_pl"]]
p_eb_te <- background_jobs_results[["p_eb_te"]]

# Plots from calculations above:
ptitle <- "Energy Balance | Numerical | Smith-Formulation" # DATEN VON OBEN HOLEN!
    
df_all_eb <- bind_rows(list(
    p_noeb$data %>% dplyr::filter(variable == "vcmax")  %>% mutate(eb_model = "no energy balance"),
    p_eb_pl$data %>% dplyr::filter(variable == "vcmax") %>% mutate(eb_model = "plantecophys"),
    p_eb_te$data %>% dplyr::filter(variable == "vcmax") %>% mutate(eb_model = "tealeaves")))

p1 <- df_all_eb %>% ggplot() +
    aes(x, y) +
    geom_abline(linetype = "dotted") +
    geom_errorbar(aes( ymin = y - vcmax_se, ymax = y + vcmax_se, color = climate_zone), alpha = 0.5) +
    geom_point(aes(color = climate_zone),
               shape = 16,
               alpha = 0.8) +
    geom_smooth(method = "lm", fullrange = T, color = "black") +
    # ggpmisc::stat_poly_eq(formula = y ~ x, aes(label = paste(..eq.label.., sep = "~~~")), vjust = 1, parse = TRUE) +
    ggpmisc::stat_poly_eq(formula = y ~ x, aes(label = paste(..rr.label.., sep = "~~~")), vjust = 1, parse = TRUE) +
    ggpmisc::stat_poly_eq(formula = y ~ x, aes(label = paste(..n.label.., sep = "~~~") ), vjust = 3, parse = TRUE) +
    facet_wrap(~eb_model) +
    xlim(0, 250) +
    ylim(0, 250) +
    scale_color_manual(values = c("#960000", "#FF0000", "#FF6E6E", "#FFCCCC",
                                  "#CC8D14", "#CCAA54", "#FFCC00", "#FFFF64",
                                  "#007800", "#005000", "#003200", "#96FF00", "#00D700", "#00AA00", "#BEBE00", "#8C8C00", "#5A5A00",
                                  "#550055", "#820082", "#C800C8", "#FF6EFF", "#646464", "#8C8C8C", "#BEBEBE", "#E6E6E6", "#6E28B4",
                                  "#B464FA", "#C89BFA", "#C8C8FF", "#6496FF",
                                  "#64FFFF", "#F5FFFF"),
                              name = "Koeppen-Geiger Climate Zone",
                              guide = guide_legend(
                                  direction = "horizontal",
                                  title.position = "top",
                                  ncol = 10)) +
    theme(legend.position = "none") +
    ylab(bquote("Observed"~V[cmax] ~ "[µmol" ~ m^-2 ~ s ^-1 ~ "]")) +
    xlab(bquote("Predicted"~V[cmax] ~ "[µmol" ~ m^-2 ~ s ^-1 ~ "]"))

## .................................................................................................
### T_growth: air vs leaf
p2 <- df_all_eb %>% 
    ggplot() +
    aes(tc_growth_air, tc_growth_leaf) +
    geom_abline(linetype = "dotted") +
    geom_errorbar(aes( ymin = tc_growth_air*1000 - 10, ymax = tc_growth_air*1000 + 10, color = climate_zone), alpha = 0.5) +
    geom_point(aes(color = climate_zone)) +
    # geom_smooth(method = "lm", fullrange = T, color = "black") +
    # ggpmisc::stat_poly_eq(formula = y ~ x, aes(label = paste(..eq.label.., sep = "~~~")), vjust = 1, parse = TRUE) +
    # ggpmisc::stat_poly_eq(formula = y ~ x, aes(label = paste(..rr.label.., sep = "~~~")), vjust = 2.25, parse = TRUE) +
    # ggpmisc::stat_poly_eq(formula = y ~ x, aes(label = paste(..n.label.., sep = "~~~") ), vjust = 5, parse = TRUE) +
    facet_wrap(~eb_model) +
    xlim(5, 35) +
    ylim(5, 35) +
    scale_color_manual(values = c("#960000", "#FF0000", "#FF6E6E", "#FFCCCC",
                                  "#CC8D14", "#CCAA54", "#FFCC00", "#FFFF64",
                                  "#007800", "#005000", "#003200", "#96FF00", "#00D700", "#00AA00", "#BEBE00", "#8C8C00", "#5A5A00",
                                  "#550055", "#820082", "#C800C8", "#FF6EFF", "#646464", "#8C8C8C", "#BEBEBE", "#E6E6E6", "#6E28B4",
                                  "#B464FA", "#C89BFA", "#C8C8FF", "#6496FF",
                                  "#64FFFF", "#F5FFFF"),
                              name = "Koeppen-Geiger Climate Zone",
                              guide = guide_legend(
                                  direction = "horizontal",
                                  title.position = "top",
                                  ncol = 10)) +
    theme(legend.position = "bottom") +
    ylab(bquote("Growth"~T[leaf] ~ "[°C]")) +
    xlab(bquote("Growth"~T[air] ~ "[°C]"))

(p <- p1 / p2 + plot_annotation(title = ptitle))

ggsave("~/projects/mscthesis/docs/fig_energybalance_facet_smith.pdf", p, height = 7, width = 8)
```

# ---


# Testzone
```{r}
## Get data
df_drivers_p21    <- readRDS("~/data/mscthesis/final/df_drivers_p21.rds")
df_evaluation_p21 <- readRDS("~/data/mscthesis/raw/leaf_traits_peng2021/df_P21_clean.rds") %>%
    dplyr::select(-author) %>%
    rename_with(tolower) %>%
    dplyr::filter(!((is.na(jmax) | is.na(vcmax))),
                  !is.na(date),
                  !is.na(lat),
                  !is.na(lon)) %>%
    group_by(site, date) %>%
    nest() %>%
    ungroup() %>%
    rename(sitename = site,
           data_raw = data)
```

```{r}
list_smith$p[[1]]
```


## Model Bias
```{r, fig.height=5, fig.width=10}
library(car)

## Analytical
### Smith
selected_df <- p_ana_s37$data
df_with_bias <- left_join(selected_df, df_drivers_p21 %>% dplyr::select(sitename, forcing) %>% unnest(forcing)) %>% dplyr::filter(variable == "vcmax") %>% mutate(bias = (x-y)/y*100)
lm_t <- lm(bias ~ tc_growth_air + tc_home + patm_growth + vpd_growth + ppfd_growth, data = df_with_bias)
crPlots(lm_t, ylim = c(-300, 300), ylab = "Bias [%]", layout = c(2,3), col.lines = c("tomato", "blue2"), smooth = FALSE, lwd = 3,
        main = "Partial Residual Plots for Model Bias - Analytical Smith 1937")

### Farquhar
selected_df <- p_ana_f89$data
df_with_bias <- left_join(selected_df, df_drivers_p21 %>% dplyr::select(sitename, forcing) %>% unnest(forcing)) %>% dplyr::filter(variable == "vcmax") %>% mutate(bias = (x-y)/y*100)
lm_t <- lm(bias ~ tc_growth_air + tc_home + patm_growth + vpd_growth + ppfd_growth, data = df_with_bias)
crPlots(lm_t, ylim = c(-300, 300), ylab = "Bias [%]", layout = c(2,3), col.lines = c("tomato", "blue2"), smooth = FALSE, lwd = 3,
        main = "Partial Residual Plots for Model Bias - Analytical Farquhar 1989")

## Numerical
### Smith
selected_df <- p_num_s37$data
df_with_bias <- left_join(selected_df, df_drivers_p21 %>% dplyr::select(sitename, forcing) %>% unnest(forcing)) %>% dplyr::filter(variable == "vcmax") %>% mutate(bias = (x-y)/y*100)
lm_t <- lm(bias ~ tc_growth_air + tc_home + patm_growth + vpd_growth + ppfd_growth, data = df_with_bias)
crPlots(lm_t, ylim = c(-300, 300), ylab = "Bias [%]", layout = c(2,3), col.lines = c("tomato", "blue2"), smooth = FALSE, lwd = 3,
        main = "Partial Residual Plots for Model Bias - Numerical Smith 1937")

### Farquhar
selected_df <- p_num_f89$data
df_with_bias <- left_join(selected_df, df_drivers_p21 %>% dplyr::select(sitename, forcing) %>% unnest(forcing)) %>% dplyr::filter(variable == "vcmax") %>% mutate(bias = (x-y)/y*100)
lm_t <- lm(bias ~ tc_growth_air + tc_home + patm_growth + vpd_growth + ppfd_growth, data = df_with_bias)
crPlots(lm_t, ylim = c(-300, 300), ylab = "Bias [%]", layout = c(2,3), col.lines = c("tomato", "blue2"), smooth = FALSE, lwd = 3,
        main = "Partial Residual Plots for Model Bias - Numerical Farquhar 1989")

```


```{r, fig.height=5, fig.width=10}
## Calculating Bias by hand (does not work because less partial residuals than x-values...):

df_bias_final <- tibble()

for (var in c("tc_growth_air", "tc_home", "elv", "vpd_growth", "ppfd_growth")) {
    
    x <- stats::predict(lm_t, type="terms", term=var)
    # x <- df_with_bias[[var]]
    y <- residuals(lm_t, type="partial")[, var]

    df_bias_final <- bind_rows(list(df_bias_final,
                                    tibble(x = x, y = y, var = var)))
}

p_bias <- df_bias_final %>% 
    ggplot() +
    aes(x, y) +
    geom_point()  + 
    geom_smooth(method = "lm", linetype = "dashed") +
    geom_smooth(method = "loess", color = "red", linetype = "dashed") +
    ylim(-200, 200) +
    ggpmisc::stat_poly_eq(data = df_bias_final, formula = y ~ x, method = "lm",
                      aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE) +
    geom_abline(slope = 0, intercept = 0) +
    facet_wrap(~var, scales = "free_x")
```


## Using all vcmax25 values, not just daily averages
```{r}
## Analytical
settings <- get_settings()
df_ana_s37   <- run_rpmodel_accl(settings = settings, df_drivers = df_drivers_p21, df_evaluation = df_evaluation_p21) 

t <- df_ana_s37 %>% unnest(c(forcing, rpm_accl)) %>% 
    rename(vcmax25_rpm = vcmax25,
           jmax25_rpm = jmax25) %>% 
    dplyr::select(sitename, date, vcmax25_rpm, jmax25_rpm, tc_growth_air, tc_home, data_raw) %>% 
    unnest(data_raw) %>% 
    mutate(vcmax = vcmax/10^6,
           jmax  = jmax/10^6,
           jmax_rpm    = jmax25_rpm  * calc_ftemp_inst_jmax(tleaf, tc_growth_air, tc_home, method_ftemp = "kumarathunge2019"),
           vcmax_rpm   = vcmax25_rpm * calc_ftemp_inst_vcmax(tleaf, tc_growth_air, method_ftemp = "kumarathunge2019"))


t %>% ggplot() +
    aes(vcmax_rpm, vcmax) +
    geom_point() +
    geom_smooth(method = "lm") +
    ylim(0, 4e-4) +
    xlim(0, 4e-4) +
    geom_abline()  +
        ggpmisc::stat_poly_eq(data = t,
                              formula = y ~ x,
                              method = "lm",
                              aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
                              parse = TRUE)

lm(vcmax ~ vcmax_rpm, data = t) %>% summary()
```
## Summary on P21 dataset
```{r}
df <- p_ana_s37$data

## Vcmax measurements:
df <- df %>% mutate(variable = as.factor(variable), sitename = as.factor(sitename))

df %>% dplyr::filter(variable == "vcmax") %>% drop_na(y) %>% summary()
df %>% dplyr::filter(variable == "jmax") %>% drop_na(y) %>% summary()

df_evaluation_p21 %>% unnest(data_raw) %>% summary()
```

```{r}
out$pvcmax
out$pjmax
```

