---
title: "Extraction of optimal temperature values from Kumarathunge et al. (2019) data"
author: "Pascal Schneider"
date: "6/23/2021"
output: html_document
---

```{r sourcing}
path = "~/data/mscthesis/raw/photom_kumarathunge2019"
```

# Notes

- I do not own the original data on the original csv-files that are wrangled below. Please see "centralscript.R" on https://bitbucket.org/Kumarathunge/photom to extract the csv-files used below
- Running all chunks in this rmarkdown extracts all data points for optimal temperature used in this thesis.
- Section names refer to the first author's last name. See metainfo file loaded at bottom of this script for more information.



# Data wrangling for aci datapoints at ambient conditions
## Setup for fits
```{r}
x <- "Tleaf"
y <- "Photo"
```

## Onoda
```{r}
df_onoda <- read_csv(paste0(path,"/aci_datapoints/Onoda_etal.csv")) %>%
  dplyr::filter(GrowthCa == "amb",
         #Photo < 8.2, Removed outliers by Dushan but don't know why
         between(Ci, 250, 350)) %>% 
  mutate(dataset = "onoda",
         Season = ifelse(Season == "May", paste(mean.Date(c(dmy("08-05-2002"), dmy("12-05-2002")))),  Season),
         Season = ifelse(Season == "August", paste(mean.Date(c(dmy("29-07-2002"), dmy("06-08-2002")))), Season),
         Season = ifelse(Season == "Oct", paste(mean.Date(c(dmy("14-10-2002"), dmy("25-10-2002")))), Season),
         sample_date = ymd(Season),
         agg_date = sample_date) %>%
  group_by(dataset,
           agg_date) %>%
  nest() %>% 
	mutate(fit_opt = purrr::map(data, ~fit_nonlinear_topt(dat = .x, x = x, y = y, random = "none")))

df_onoda %>% unnest(cols = "fit_opt") %>% dplyr::select(dataset, data, agg_date, pvalue)
```

## Cernusak
```{r}
df_sav <- read_csv(paste(path,"/aci_datapoints/SIOP Leaf gas exchange Cernusak et al.csv", sep="")) %>% 
  dplyr::filter(between(CO2R, 390, 410), # Only use data taken at ambient CO2
         Canopy_position == "Canopy", # Only use leaves at canopy level
         PARi > 1800) %>% # Only use data at light-saturation
  mutate(dataset = "savanna",
         sample_date = dmy(Date),
         agg_date = sample_date) %>% 
  group_by(dataset,
           agg_date) %>%
  nest() %>% 
	mutate(fit_opt = purrr::map(data, ~fit_nonlinear_topt(dat = .x, x = x, y = y, random = "Leaf_number")))

df_sav %>% unnest(cols = "fit_opt") %>% dplyr::select(dataset, fit_method, agg_date, pvalue)
```

## Kelly
```{r}
df_kelly <- read_csv(paste(path,"/aci_datapoints/Daintree_ACidata_processed.csv", sep="")) %>% 
  dplyr::filter(between(CO2R, 375, 425),  # Only use data taken at ambient CO2
                Ci > 175) %>% # QC by Kumarathunge2019
  mutate(dataset = "kelly",
         Season = ifelse(Season == "SUMMER", "2011-04-07", Season), 
         Season = ifelse(Season == "WINTER", "2010-07-22", Season),  
         sample_date = ymd(Season),
         agg_date = sample_date) %>% 
  group_by(dataset,
           agg_date) %>%
  nest() %>% 
	mutate(fit_opt = purrr::map(data, ~fit_nonlinear_topt(dat = .x, x = x, y = y, random = "Spp")))

df_kelly %>% unnest(cols = "fit_opt") %>% dplyr::select(dataset, fit_method, agg_date, pvalue)
```

## Togashi
```{r}
df_togashi <- read_csv(paste(path,"/aci_datapoints/gwwACidata_processed_new.csv", sep="")) %>% 
  dplyr::filter(between(Ci,365, 435),
         !(Curve %in% c(19,23,27,44))) %>% 
  mutate(dataset = "togashi",
         Season = ifelse(Season == "Summer", "2017-06-21", Season),  # Assumed winter and summer mid in southern hemisphere, Kumarathunge used "2013-04-04" for all fits to get Tavg_30
         Season = ifelse(Season == "Winter", "2017-12-21", Season),  # Year of publication assumed, southern hemisphere mid-season assumed
         sample_date = ymd(Season),
         agg_date = sample_date) %>% 
  group_by(dataset,
           agg_date) %>%
  nest() %>% 
	mutate(fit_opt = purrr::map(data, ~fit_nonlinear_topt(dat = .x, x = x, y = y, random = "Tree")))

df_togashi %>% unnest(cols = "fit_opt") %>% dplyr::select(dataset, fit_method, agg_date, pvalue)
```

## Medlyn (eucalypt)
```{r}
df_medlyn_eucalypt <- read_csv(paste(path,"/aci_datapoints/TumbarumbaGasex_Spot_Medlyn.csv", sep="")) %>% 
  dplyr::filter(PARi > 1200,
         Cond > 0.09) %>% 
  mutate(dataset = "medlyn_eucalypt",
         sample_date = dmy(Date),
         agg_date = round_date(sample_date, unit = "week")) %>% 
  group_by(dataset,
           agg_date) %>%
  nest() %>% 
	mutate(fit_opt = purrr::map(data, ~fit_nonlinear_topt(dat = .x, x = x, y = y, random = "Age Class")))

df_medlyn_eucalypt %>% unnest(cols = "fit_opt") %>% dplyr::select(dataset, fit_method, agg_date, pvalue)
```

## UWS (eucface)
```{r}
df_eucface <- read_csv(paste(path,"/aci_datapoints/eucFace_data.csv", sep="")) %>% 
   group_by(Curve) %>%
   arrange(Obs) %>%
   slice(1) %>%
   ungroup %>% 
   dplyr::filter(!(Tree %in% c(2,7)),
          between(CO2R, 400, 430),
          CO2S > 100) %>% 
   mutate(dataset = "eucface",
          sample_date = NA,
          agg_date = sample_date) %>% 
   group_by(dataset,
    agg_date) %>%
   nest() %>% 
	mutate(fit_opt = purrr::map(data, ~fit_nonlinear_topt(dat = .x, x = x, y = y, random = "Tree")))

df_eucface %>% unnest(cols = "fit_opt") %>% dplyr::select(dataset, fit_method, agg_date, pvalue)
```

## Slot
```{r}
df_slot <- read_csv(paste(path,"/aci_datapoints/SlotWinter2017_NewPhyt.Data.csv", sep="")) %>% 
  dplyr::filter(Form == "Tree") %>%  
  mutate(dataset = "slot",
         sample_date = dmy(Date),
         # agg_date = round_date(sample_date, unit = "week"), 
         agg_date = sample_date) %>% # Daily resolution preferred
  group_by(dataset,
           agg_date) %>%
  nest() %>% 
	mutate(fit_opt = purrr::map(data, ~fit_nonlinear_topt(dat = .x, x = x, y = y, random = "Species")))

df_slot %>% unnest(cols = "fit_opt") %>% dplyr::select(dataset, data, agg_date, pvalue, r2) %>% arrange(pvalue)
```

## Tribuzy
```{r}
df_tribuzi <- read_csv(paste(path,"/aci_datapoints/AmazonACIdata_f.csv", sep="")) %>% 
  dplyr::filter(between(Ci, 175, 270)) %>%  
  mutate(dataset = "tribuzi",
         Season = ifelse(Season == "wet", "2005-04-15", Season), # wet/dry but no actual information found
         Season = ifelse(Season == "dry", "2005-10-15", Season),
         sample_date = ymd(Season), 
         agg_date = sample_date) %>% 
  group_by(dataset,
           agg_date) %>%
  nest() %>% 
  	mutate(fit_opt = purrr::map(data, ~fit_nonlinear_topt(dat = .x, x = x, y = y, random = "Species")))

df_tribuzi %>% unnest(cols = "fit_opt") %>% dplyr::select(dataset, b, fit_method, topt, agg_date, pvalue)
```

## Wang
```{r}
df_wang <- read_csv(paste0(path,"/aci_datapoints/Betula_pendula_Pinus_sylvestris_wang_etal.csv")) %>%
  dplyr::filter(between(Ci, 240, 400),
                !(Species == "Betula pendula")) %>%
  mutate(dataset = "wang",
         sample_date = dmy(ifelse(Date == "Jul-98", "15-07-1994", Date)),
         agg_date = sample_date) %>% 
  group_by(dataset,
           agg_date) %>%
  nest() %>% 
  	mutate(fit_opt = purrr::map(data, ~fit_nonlinear_topt(dat = .x, x = x, y = y, random = "Leaf")))

df_wang %>% unnest(cols = "fit_opt") %>% dplyr::select(dataset, fit_method, agg_date, pvalue, r2)
```

## UWS (whole-tree-chamber)
```{r}
df_wtc <- bind_rows(read_csv(paste0(path,"/aci_fits/wtc1.csv")) %>%
                      mutate(dataset = "wtc1",
                             Date = ymd(ifelse(Season == "January", "2010-01-01", "2010-11-01"))) %>%
                      dplyr::filter(CO2_Treat == "Ambient",
                             Water_treat == "wet",
                             between(CO2S, 380, 420),
                             Tleaf > 21),
                    
                    read_csv(paste0(path,"/aci_fits/wtc2.csv")) %>%
                      mutate(dataset = "wtc2",
                             Date = ymd(Date)) %>%
                      dplyr::filter(C_treat=="0C",
                             between(Ci, 70, 330),
                             CO2R > 40),
                
                    read_csv(paste0(path,"/aci_fits/wtc3.csv")) %>% 
                      mutate(dataset = "wtc3",
                             Date = dmy(Date)) %>%
                      dplyr::filter(Treatment == "Ambient",
                             between(Ci, 110, 390),
                             CO2S > 350,
                             !(MeanTemp == "14-Apr" & Chamber == 5)),
                    
                    read_csv(paste0(path,"/aci_fits/wtc4.csv")) %>% 
                      mutate(dataset = "wtc4",
                             Date = dmy(Date)) %>%  
                      dplyr::filter(Temp_Treatment == "ambient")) %>% 
  
  mutate(dataset = "wtc",
         sample_date = Date,
         agg_date = round_date(sample_date, unit = "week")) %>% 
  group_by(dataset,
           agg_date) %>%
  nest() %>% 
  	mutate(fit_opt = purrr::map(data, ~fit_nonlinear_topt(dat = .x, x = x, y = y, random = "Chamber")))

df_wtc %>% unnest(cols = "fit_opt") %>% dplyr::select(dataset, fit_method, b, agg_date, pvalue) %>% arrange(pvalue)
```

## Han (cypress)
```{r}
df_han_cypress <- read_csv(paste0(path,"/aci_datapoints/Chamaecyparis obtusa_han_etal.csv")) %>%
  dplyr::filter(between(Ci, 175, 230)) %>% 
  mutate(dataset = "han_cypress",
         sample_date = my(paste0(Season, "2004")),
         agg_date = sample_date) %>% 
  group_by(dataset,
          agg_date) %>%
  nest() %>% 
  	mutate(fit_opt = purrr::map(data, ~fit_nonlinear_topt(dat = .x, x = x, y = y, random = "none")))

df_han_cypress %>% unnest(cols = "fit_opt") %>% dplyr::select(dataset, agg_date, pvalue)
```

## Medlyn (pine)
```{r}
df_medlyn_pine <- read_csv(paste(path,"/aci_datapoints/Medlyn_etal_all.csv", sep="")) %>% 
  dplyr::filter(between(Ci, 175, 350),
         Curve != 62,
         !(Species == "Landes" & Season == "Jun"),
         !(Species == "Tamjoute")) %>%
  mutate(dataset = "medlyn_pine",
         Species = ifelse(Species == "Landes", "Pinus pinaster_L", Species),
         Season = ifelse(Season == "Jul", paste(mean.Date(c(dmy("29/6/1999"), dmy("8/7/1999")))),  Season),
         Season = ifelse(Season == "AugSept", paste(mean.Date(c(dmy("24/8/1999"), dmy("1/9/1999")))), Season),
         Season = ifelse(Season == "Nov", paste(mean.Date(c(dmy("16/11/1999"), dmy("25/11/1999")))), Season),
         Season = ifelse(Season == "Jan", paste(mean.Date(c(dmy("25/1/2000"), dmy("1/2/2000")))), Season),
         Season = ifelse(Season == "Mar", paste(mean.Date(c(dmy("27/3/2000"), dmy("3/4/2000")))), Season),
         Season = ifelse(Season == "Jun", paste(mean.Date(c(dmy("7/6/2000"), dmy("14/6/2000")))), Season),
         Season = ifelse(Season == "Oct", paste(mean.Date(c(dmy("17/10/2000"), dmy("26/10/2000")))), Season),
         sample_date = ymd(Season),
         agg_date = sample_date) %>% 
  group_by(dataset,
           agg_date) %>%
  nest() %>% 
  	mutate(fit_opt = purrr::map(data, ~fit_nonlinear_topt(dat = .x, x = x, y = y, random = "Leaf")))

df_medlyn_pine %>% unnest(cols = "fit_opt") %>% dplyr::select(dataset, data, agg_date, pvalue)
```

## Tarvainen (spruce)
```{r}
df_tarvainen_spruce <- read_csv(paste(path,"/aci_datapoints/Pieca_abies_tarvainen_etal.csv", sep="")) %>% 
  dplyr::filter(between(CO2R, 395, 405)) %>%  
  mutate(dataset = "tarvainen_spruce",
         Season = ifelse(Season == "Year1", "2009-06-15", Season),
         Season = ifelse(Season == "Year3", "2009-09-15", Season),
         sample_date = ymd(Season),
         agg_date = sample_date) %>% 
  group_by(dataset,
           agg_date) %>%
  nest() %>% 
  	mutate(fit_opt = purrr::map(data, ~fit_nonlinear_topt(dat = .x, x = x, y = y, random = "Tree")))

df_tarvainen_spruce %>% unnest(cols = "fit_opt") %>% dplyr::select(dataset, data, agg_date, pvalue)
```

## Han (pine)
```{r}
df_han_pine <- read_csv(paste(path,"/aci_datapoints/Pinus_densiflora_han_etal.csv", sep="")) %>% 
  dplyr::filter(between(CO2S, 330, 350)) %>%
  mutate(dataset = "han_pine",
         sample_date = ifelse(Season == "May",paste0("15-", Season, "-2002"), paste0("15-", Season, "-2001")),
         sample_date = dmy(sample_date),
         agg_date = sample_date) %>% 
  group_by(dataset,
          agg_date) %>%
  nest() %>% 
  mutate(fit_opt = purrr::map(data, ~fit_nonlinear_topt(dat = .x, x = x, y = y, random = "Leaf")))

df_han_pine %>% unnest(cols = "fit_opt") %>% dplyr::select(dataset, fit_method, agg_date, pvalue)
```

## Ellsworth
```{r}
df_ellsworth <- read_csv(paste(path,"/aci_datapoints/Pteada_Ellsworth.csv", sep="")) %>% 
  # Quality control as done by Kumarathunge2019
  dplyr::filter(between(CO2S, 340, 370)) %>%
  mutate(dataset = "ellsworth",
         sample_date = dmy(paste("15-", Date)),
         agg_date = sample_date) %>% 
  group_by(dataset,
          agg_date) %>%
  nest() %>% 
  	mutate(fit_opt = purrr::map(data, ~fit_nonlinear_topt(dat = .x, x = x, y = y, random = "Leaf")))

df_ellsworth %>% unnest(cols = "fit_opt") %>% dplyr::select(dataset, data, agg_date, pvalue)
```

## Rogers
```{r}
df_arctic <- read_csv(paste(path,"/aci_datapoints/Arctic_A-Ci_curves_2012-2015_V2.csv", sep="")) %>% 
  # Quality control as done by Kumarathunge2019
  dplyr::filter(between(CO2S, 370, 410)) %>%
  mutate(dataset = "arctic",
         sample_date = ymd(Sample_Date),
         agg_date = round_date(sample_date, unit = "week")) %>% 
  group_by(dataset,
           agg_date) %>% 
  nest() %>% 
  	mutate(fit_opt = purrr::map(data, ~fit_nonlinear_topt(dat = .x, x = x, y = y, random = "USDA_Species_Code")))

df_arctic %>% unnest(cols = "fit_opt") %>% dplyr::select(dataset, data, agg_date, pvalue)
```

## Anna
```{r}
df_anna <- read_csv(paste(path,"/aci_datapoints/SPRUCE_3_cohort_ACi_data.csv", sep="")) %>% 
  dplyr::filter(between(CO2R, 395, 410),
         Month %in% c(8, 10)) %>% 
  mutate(dataset = "anna",
         sample_date = as_date(DOY-1, origin = paste0(Year, "-01-01")),  # Converting DOY and year information into day, -1 needed because as_date takes 0 as 1. January)
         agg_date = sample_date) %>% 
  group_by(dataset,
           agg_date) %>%
  nest() %>% 
  mutate(fit_opt = purrr::map(.x = data, .f = ~fit_nonlinear_topt(dat = .x, x = x, y = y, random = "Cohort_age")))

df_anna %>% unnest(cols = "fit_opt") %>% dplyr::select(dataset, data, agg_date, pvalue)
```

## Carter
```{r}
df_kelsey <- read_csv(paste(path,"/aci_datapoints/kelsey_cater_Aci_PuertoRico.csv", sep="")) %>% 
  group_by(Curve) %>%
  arrange(Obs) %>%
  slice(1) %>%
  ungroup %>% 
  mutate(dataset = "kelsey",
         sample_date = dmy(Date),
         agg_date = sample_date) %>% 
  group_by(dataset,
           agg_date) %>%
  nest() %>% 
  	mutate(fit_opt = purrr::map(data, ~fit_nonlinear_topt(dat = .x, x = x, y = y, random = "Species")))

df_kelsey %>% unnest(cols = "fit_opt") %>% dplyr::select(dataset, data, agg_date, pvalue)
```

## Mau
```{r}
df_alida <- read_csv(paste(path,"/aci_datapoints/alida_mao_Aci_PuertoRico.csv", sep="")) %>% 
  group_by(Curve) %>%
  arrange(Obs) %>%
  slice(1) %>%
  ungroup %>% 
  mutate(dataset = "alida",
    sample_date = dmy(date),
    agg_date = floor_date(sample_date, unit = "month")) %>% 
  group_by(dataset,
           agg_date) %>% 
  nest() %>% 
  	mutate(fit_opt = purrr::map(data, ~fit_nonlinear_topt(dat = .x, x = x, y = y, random = "Species")))

df_alida %>% unnest(cols = "fit_opt") %>% dplyr::select(dataset, agg_date, pvalue)
```

## Hikosaka
```{r}
df_hikosaka <- read_csv(paste(path,"/aci_datapoints/hikosaka_aci_data.csv", sep="")) %>% 
  dplyr::filter(between(CO2S, 360, 375),
         !(Curve %in% c(108:110,115:117))) %>% 
  mutate(dataset = "hikosaka",
         Date = ifelse(Date == "2001-06-01", "2001-06-11", Date), 
         Date = ifelse(Date == "2001-08-01", "2001-08-10", Date), 
         Date = ifelse(Date == "2001-09-01", "2001-09-20", Date), 
         Date = ifelse(Date == "2002-06-01", "2002-06-10", Date), 
         Date = ifelse(Date == "2002-07-01", "2002-07-29", Date), 
         Date = ifelse(Date == "2002-09-01", "2002-09-28", Date), 
         sample_date = dmy(Date),
         agg_date = sample_date) %>% 
  group_by(dataset,
           agg_date) %>%
  nest() %>% 
  	mutate(fit_opt = purrr::map(data, ~fit_nonlinear_topt(dat = .x, x = x, y = y, random = "none")))

df_hikosaka %>% unnest(cols = "fit_opt") %>% dplyr::select(dataset, data, agg_date, pvalue)
```

## Tarvainen (pine)
```{r}
df_tarvainen_pine <- read_csv(paste(path,"/aci_datapoints/scots_pine_tarvainen.csv", sep="")) %>% 
  dplyr::filter(between(CO2R, 395, 410)) %>% 
  mutate(dataset = "tarvainen_pine",
         sample_date = dmy(paste0(Date, "2013")),
         agg_date = sample_date) %>%
  group_by(dataset,
           agg_date) %>%
  nest() %>% 
  	mutate(fit_opt = purrr::map(data, ~fit_nonlinear_topt(dat = .x, x = x, y = y, random = "Tree")))

df_tarvainen_pine %>% unnest(cols = "fit_opt") %>% dplyr::select(dataset, data, agg_date, pvalue, r2) %>% arrange(pvalue)
```

## Binding all datasets
```{r}
df_obs_opt <- bind_rows(list(
                         df_alida,
                         df_anna,
                         df_arctic,
                         df_ellsworth,
                         df_eucface,
                         df_han_cypress,
                         df_han_pine,
                         df_hikosaka,
                         df_kelly,
                         df_kelsey,
                         df_medlyn_eucalypt,
                         df_medlyn_pine,
                         df_onoda,
                         df_sav,
                         df_slot,
                         df_tarvainen_pine,
                         df_tarvainen_spruce,
                         df_togashi,
                         df_tribuzi,
                         df_wang,
                         df_wtc
                         )) %>% 
  
  ## Quality Check
  unnest(fit_opt) %>% 
  drop_na(topt, agg_date) %>% # Exclude NA fits and fits without date
  nest(fit_opt = c("aopt", "aopt.se", "topt", "topt.se", "b", "b.se", "r2", "s", "pvalue", "fit_method")) %>% 
  ungroup()

saveRDS(df_obs_opt, "~/data/mscthesis/raw/photom_kumarathunge2019/df_obs_opt_preQC.rds")
```

# Quality Control
## Summary before QC
```{r}
cat("\n Fixed Ci: --------------------------------------")
pval <- 0.1
all  <- df_obs_qc %>% nrow
sign <- df_obs_qc %>% unnest(cols = "fit_opt") %>% dplyr::filter(pvalue < pval) %>% nrow()
cat("\n p-values below", pval*100,"%: ", sign, "/", all, "| which is", round(sign/all, 2)*100, "% \n")
```

## Create plots pre QC
```{r}
subset <- "obs"
df_1 <- readRDS(paste0("data/figures_topt_extraction/", subset, "_opt_preQC.rds"))

for (i in 1:nrow(df_1)) {

	cat('\014')
	cat(paste0(subset, " | ", round(i / nrow(df_1) * 100), "% completed \n "))

	df_i <- df_1 %>%
		slice(i) %>%
		unnest(c(data, fit_opt)) %>%
		mutate(sample_date = as.factor(sample_date))

	site       <- df_i$dataset[1]
	date       <- df_i$agg_date[1]
	fit_method <- df_i$fit_method[1]
	r2         <- round(df_i$r2[1], 2)
	pval       <- round(df_i$pvalue[1], 2)
	tc_opt     <- round(df_i$topt[1], 2)
	tc_opt_se  <- round(df_i$topt.se[1], 2)
	
	df_i$y <- df_i[[y]]
	df_i$x <- df_i[[x]]
	
	df_2 <- tibble(
		tleaf = seq(0, 50, 0.1),
		anet = df_i$aopt[1] - ( df_i$b[1] * ( tleaf - df_i$topt[1]) ^ 2))
	
	# For easy plotting:
	coef_1 <- df_i[1, ]

	
	# Plot it
	p <- ggplot() +
		geom_point(data = df_i, aes(x = x, y = y, color = sample_date)) +
		geom_line( data = df_2, aes(x = tleaf, y = anet)) +
		geom_point(data = coef_1,aes(x = topt, y = aopt), color = "red") + # shape = 18, size = 4
		geom_errorbarh(data = coef_1, aes(y = aopt, xmin = topt - topt.se, xmax = topt + topt.se), color = "red") +
		geom_errorbar( data = coef_1, aes(x = topt, ymin = aopt - aopt.se, ymax = aopt + aopt.se), color = "red") +
		xlim(0, 50) +
		ylim(0, 30) +
		ylab(bquote("Net Assimilation ["~mu~mol ~CO[2]~ m^-2~s^-1~"]")) +
		xlab(bquote("Leaf Temperature [°C]")) +
		labs(color = "Sampling Date",
				 title = paste0(subset, " | ", site, " | ", date, " | tc_opt: ", tc_opt, " +- ", tc_opt_se),
				 subtitle = paste0(fit_method, " | p = ", pval, " | r2 = ", r2)) +
		scale_color_brewer(palette = "Dark2")

	# Save it
	ggsave(paste0("~/data/mscthesis/raw/photom_kumarathunge2019/pre_QC/", subset, "_", site, "_", date, ".png"), p, width = 8, height = 8, units = "in")
}
```

## QC Selection
```{r}
# Criteria for exclusion based on visual inspection:
## (1): Non-sensible fit compared to data points, e.g.:
##      - Parabola misses optimal temperature that is well-shown by data points
##      - Fit is defined by one outlier
##      - Ecophysiologically impossible optimal temperature
##
## (2): Non-sensible distribution of data points
##      - Zero assimilation rate over multiple leaf temperatures (estimate is middle of temperature range)
##      - Too narrow range in leaf temperatures for sensible fit
df_obs_qc <- readRDS("~/data/mscthesis/raw/photom_kumarathunge2019/df_obs_opt_preQC.rds") %>% 
	dplyr::filter(!(dataset == "anna" & agg_date == "2013-08-03"), # (2) TODO: Could be revised by checking why two curves are visible
								!(dataset == "anna" & agg_date == "2013-08-04"), # (2)
								!(dataset == "kelsey" & agg_date == "2015-07-03"), # (2)
								!(dataset == "kelsey" & agg_date == "2015-07-09"), # (2)
								!(dataset == "kelsey" & agg_date == "2015-07-15"), # (1)
								!(dataset == "kelsey" & agg_date == "2015-07-17"), # (1)
								!(dataset == "kelsey" & agg_date == "2015-07-21"), # (2)
								!(dataset == "medlyn_eucalypt" & agg_date == "2001-11-18"), # (2)
								!(dataset == "onoda" & agg_date == "2002-08-02"), # (1)
								!(dataset == "tarvainen_pine" & agg_date == "2013-08-09"), # (1) TODO: Could be included despite high s.e. and bad fit-metrics
								!(dataset == "wtc" & agg_date == "2011-02-06"), # (2) Could be revised by excluding linearly decreasing outliers
								!(dataset == "wtc" & agg_date == "2014-01-12"), # (2)
								!(dataset == "wtc" & agg_date == "2016-10-02"), # (2)
								)
```

# Saving final dataframes
```{r}
# Attach metadata
metainfo_k19 <- read_csv("~/data/mscthesis/final/metainfo_k19.csv")
df_obs_qc <- df_obs_qc %>%
    rename(data_raw = data) %>% 
    mutate(data_raw = purrr::map(data_raw, ~ .x %>% mutate_all(as.character))) %>% 
    left_join(metainfo_k19, by = "dataset") %>% 
    group_by(dataset, agg_date, data_raw, fit_opt) %>% 
    nest() %>% 
    ungroup() %>% 
    mutate(tc_opt_obs = purrr::map_dbl(fit_opt, ~dplyr::select(., topt) %>% pull)) %>% 
    rename(metainfo = data,
           sitename = dataset,
           date     = agg_date) %>% 
    dplyr::select(sitename, date, tc_opt_obs, fit_opt, metainfo, data_raw)
    
# saveRDS(df_275_qc, "~/data/mscthesis/final/df_275_opt_postQC.rds")
# saveRDS(df_obs_qc, "~/data/mscthesis/final/df_obs_opt_postQC.rds")
# df_obs_qc <- readRDS("~/data/mscthesis/final/df_obs_opt_postQC.rds")
```

## Summary post QC
```{r}
cat("\n QC: --------------------------------------------",
		"\n Fits removed from free  Ci dataset:", nrow(df_obs_opt) - nrow(df_obs_qc), "\n")

cat("\n Free Ci: --------------------------------------")
pval <- 0.1
all  <- df_obs_qc %>% nrow
sign <- df_obs_qc %>% unnest(cols = "fit_opt") %>% dplyr::filter(pvalue < pval) %>% nrow()
cat("\n p-values below", pval*100,"%: ", sign, "/", all, "| which is", round(sign/all, 2)*100, "% \n")
```

## Create plots post QC
```{r}
if (F) {
    for (subset in c("obs", "275")) {
    	if (subset == "obs") {
    		x <- "Tleaf"
    		y <- "Photo"
    	} else {
    		x <- "Ts"
    		y <- "lowAs"
    	}
    
    	df_1 <- readRDS(paste0("~/data/mscthesis/df_", subset, "_opt_postQC.rds"))
    
    	for (i in 1:nrow(df_1)) {
    
    		cat('\014')
    		cat(paste0(subset, " | ", round(i / nrow(df_1) * 100), "% completed \n "))
    
    		df_i <- df_1 %>%
    			slice(i) %>%
    			unnest(c(metainfo, fit_opt, data_raw)) %>%
    			mutate(sample_date = as.factor(sample_date),
    			       Tleaf = as.double(Tleaf),
    			       aopt = as.double(aopt),
    			       sitename = as.factor(sitename))
    
    		site       <- as.character(df_i$sitename[1])
    		date       <- as.character(df_i$sample_date[1])
    		fit_method <- as.character(df_i$fit_method[1])
    		r2         <- round(df_i$r2[1], 2)
    		pval       <- round(df_i$pvalue[1], 2)
    		tc_opt     <- round(df_i$topt[1], 2)
    		tc_opt_se  <- round(df_i$topt.se[1], 2)
    		
    		df_i$y <- as.double(df_i[[y]])
    		df_i$x <- as.double(df_i[[x]])
    		
    		df_2 <- tibble(
    			tleaf = seq(0, 50, 0.1),
    			anet = df_i$aopt[1] - ( df_i$b[1] * ( tleaf - df_i$topt[1]) ^ 2))
    		
    		# For easy plotting:
    		coef_1 <- df_i[1, ]
    
    		
    		# Plot it
    		p <- ggplot() +
    			geom_point(data = df_i,  aes(x = x, y = y, color = sample_date)) +
    			geom_line( data = df_2,  aes(x = tleaf, y = anet)) +
    			geom_point(data = coef_1,aes(x = topt, y = aopt), color = "red") + # shape = 18, size = 4
    			geom_errorbarh(data = coef_1, aes(y = aopt, xmin = topt - topt.se, xmax = topt + topt.se), color = "red") +
    			geom_errorbar( data = coef_1, aes(x = topt, ymin = aopt - aopt.se, ymax = aopt + aopt.se), color = "red") +
    			xlim(0, 30) +
    			ylim(0, 35) +
    			ylab(bquote("Net Assimilation [µmol"~CO[2]~ m^-2~s^-1~"]")) +
    			xlab(bquote("Leaf Temperature [°C]")) +
    			# labs(color = "Sampling Date",
    			# 		 title = paste0(subset, " | ", site, " | ", date, " | tc_opt: ", tc_opt, " +- ", tc_opt_se),
    			# 		 subtitle = bquote("Model fit: " ~ .(fit_method), " | p-value for  = " ~ pval, " | r2 = " ~ r2)) +
    			labs(color = "Sampling Date",
    			     title = "Example for date-wise aggregation of measurements",
    			     subtitle = bquote("Model fit: " ~ .(fit_method) ~ " | p-value for" ~ T[opt] ~ "<" ~ .(pval) ~ " | "~R^2 ~ " = " ~ .(r2))) +
    		    scale_color_brewer(palette = "Dark2")
    
    		# Save it
    		ggsave(paste0("~/data/mscthesis/final/plots/extracted_topt_postQC", subset, "_", site, "_", date, ".png"), p, width = 8, height = 8, units = "in")
    	}
    }
}
```

# Example plot for aggregatoion
```{r fig.height=4, fig.width=6}
# run loop above for subset = "obs" and i = "14"
p
# ggsave("~/projects/mscthesis/docs/fig-aggdate-example.pdf", p, height = 5, width = 6)
```

# Table for appendix
```{r}
## Note that "df_obs_qc" holds datasets that do not belong to the "mature native environment" dataset
df_obs_qc <- readRDS("~/data/mscthesis/final/df_obs_opt_postQC.rds") %>% dplyr::filter(str_detect(plant_env, "MNE"))

## Number of total data points
df_obs_qc %>% unnest(metainfo) %>% unnest(data_raw, names_repair = "unique") %>% nrow()

## Number of sample dates
df_obs_qc %>% unnest(metainfo) %>% unnest(data_raw, names_repair = "unique") %>% pull(sample_date) %>% unique () %>% length()

## Number of aggregation dates (equal to number of extracted topt fits)
df_obs_qc %>% unnest(metainfo) %>% pull(date) %>% unique() %>% length()

## Number of sites
df_obs_qc %>% unnest(metainfo) %>% pull(sitename) %>% unique() %>% length()

## Remaining information:
(table_topt_agg <- df_obs_qc %>% unnest(metainfo) %>% 
    dplyr::filter(str_detect(plant_env, "MNE")) %>% 
    group_by(sitename, lat, lon, source) %>% 
    nest() %>% 
    mutate(n_topt_obs = purrr::map_dbl(data, ~nrow(.))) %>% 
    dplyr::select(source, sitename, lat, lon, n_topt_obs))
```

